---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

options(help_type = "text")
```
# tl

[![Travis build status](https://travis-ci.org/ropenscilabs/tl.svg?branch=master)](https://travis-ci.org/ropenscilabs/tl)
[![Codecov test coverage](https://codecov.io/gh/ropenscilabs/tl/branch/master/graph/badge.svg)](https://codecov.io/gh/ropenscilabs/tl?branch=master)

The goal of tl is to provide an R equivalent to the tldr command line tool, a community-contributed set of quick reference guides for R functions. 

> "Perfection is achieved not when there is nothing more to add, but when there is nothing left to take away" - Antoine de Saint-Exupéry

Briefly forgotten how a function works? 
Don't want to scroll through a long help file to find the example usage? 
You need tl;dr!


## Installation

You can install the current version of tl from [github](https://github.com) with:

``` r
devtools::install_github("ropenscilabs/tl")
```

## Examples

Here are some basic examples of how to use tl:

Use the `dr` function to find a help page

```{r example, eval=TRUE}
tl:::dr(lm)

tl::dr(tidyr::gather)
```

Page you are looking for does not exist?
Use the `create_page` function to make one! Please follow the instructions to keep it brief.

```{r example2, eval=FALSE}
tl::create_page(base::system.file)
```

Want to submit your new page to the `tl` package?
Use the `submit_page` function to get instructions on how to add your help page to `tl`

```{r example3, eval=FALSE}
tl::submit_page(base::system.file)
```

